### 2016-01-20 paper.tex
Move wake paragraph in conclusion after strut drag
Remove unnecessary words

@@

The effects of parasitic drag from blade support struts on turbine performance
were measured by rotating the turbine without blades while stationary and while
towing. It is shown that these losses---even for a streamlined hydrofoil
strut---can become significant quickly at higher tip speed ratios---up to an
approximate 5 percentage point decrease in power coefficient at a tip speed
ratio of 5. These measurements were repeated with a set of high-drag cylindrical
struts, which as expected, prevented the turbine from producing any mechanical
power at any tip speed ratio. Nevertheless these measurements provide important
validation data for both high and low fidelity numerical performance prediction
models, allowing researchers and engineers to test predictions without blade
effects.

>>>>

The effects of parasitic drag from blade support struts on turbine performance
were measured by rotating the turbine without blades while stationary and while
towing. These losses---even for a streamlined hydrofoil strut---can become
significant at higher tip speed ratios---up to an approximate 5 percentage point
decrease in power coefficient at a tip speed ratio of 5. These measurements were
repeated with a set of high-drag cylindrical struts, which as expected,
prevented the turbine from producing any mechanical power at any tip speed
ratio. Nevertheless these measurements provide important validation data for
both high and low fidelity numerical performance prediction models, allowing
researchers and engineers to test predictions without blade effects.

@@
